Visualization of [fulle name] Fractional Integrals

### 2019-04-30 fractional/CMJ style files/article-template.tex
added more text to example section

Varying both $\alpha$ and $t$ results in Eq.~\ref{eq:ex1}. Eq. can be associated with a multitude of regions. Let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$. The regions in the set $\mathsf{R}_{\mathsf{T}}$ 
are depicted in Fig.~\textbf{??}. The regions in Fig that are depicted in the same panel were generated by varying $t$, whilst fixing the value of $\alpha$.

>>>>

Varying both $\alpha$ and $t$ results in Eq.~\ref{eq:ex1}. Eq. can be associated with a multitude of regions. Let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$. The regions in the set $\mathsf{R}_{\mathsf{T}}$ 
are depicted in Fig.~\textbf{??}. The regions that are depicted in each of the panels of Fig.~\ref{??} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed. 
The title of each panel indicate which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each 
panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted 
the larger the $t$-value is that was used to generate it.

Each of the regions depicted in Fig.~\ref{} are made up of an infinite number of infinitesimals, the shape of which is determined by their right edges, i.e. by the value 
of both $\alpha$ and $t$. The notion that $t$ alters the shape of the infinitesimals can easily be confirmed through visual inspection. The 
dashed grey curves and the solid grey-tinted curves in the right-most panel are not the same, i.e.$\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.

that make up the regions in Fig are confirmed by the following observation: $\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
We can visually verify that this observation is in fact true for $alpha=\frac{4}{5}$ by inspecting the right-most panel in Fig.~\ref{??}. The dashed curves and the grey tinted curves in this panel do not allign.

the upper limit 
of the Cavalieri integral in Eq. As the upper limit of the Cavalieri integral depends on

As the shape of the infinitesimals which make up the regions depicted in Fig depend of the integration limit of the 
Cavalieri integral or stated differently on the value of $t$ and $\alpha$.
